---
title: "Analysis_2"
output: 
  rmarkdown::html_vignette:
    fig_height: 7
    fig_width: 7
vignette: >
  %\VignetteIndexEntry{Analysis_2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StormR)

# Set Graphics
par(mfrow = c(1, 1))
```

# Is the number of landfalling hurricanes increasing over time? 

In this question, we try to estimate the change in the number of landfalling hurricanes over time.
Here, we will use the Hurdat dataset to answer this question. The Hurdat dataset contains
information about all the hurricanes that have occurred in the Atlantic Ocean since 1851. 

Given the large heterogeneity in the number of hurricanes that occur each month, we will
collapse the data to yearly counts, counting occurrences of each year. We will then plot the
yearly counts as a scatterplot and a histogram. We do this to understand the distribution of
the yearly counts. 

Per theory (that the number of hurricane landfalls in a year is count data), we expect the
distribution of the yearly counts to be Poisson. We can test this by observing the histogram
of the yearly counts and comparing it to the Poisson distribution overlayed on the plot. We also note that the
mean and variance of the yearly counts are similar, as theory predicts.

Thus, we can conclude that the yearly counts are Poisson distributed. Given this information, we
can fit a Poisson regression model to the data. We will use the year as the predictor variable
and the yearly counts as the response variable. We will then plot the model on a scatterplot
of the data. 

The Poisson regression model is a generalized linear model (GLM) that assumes the response
variable is Poisson distributed. The Poisson distribution is a discrete probability distribution
that expresses the probability of a given number of events occurring in a fixed interval of time
or space if these events occur with a known constant mean rate and independently of the time
since the last event. The Poisson distribution can be used to model the number of events
occurring in a given time interval.

The Poisson regression model specified in this question is as follows, where $Y_i$ is the number
of landfalling hurricanes in year $i$, $X_i$ is the year, and $\lambda_i$ is the mean number of
landfalling hurricanes in year $i$: 

$$
\begin{align}
Y_i &\sim Poisson(\lambda_i) \\
\end{align}
$$

Thus, the mean of the Poisson distribution is $\lambda_i$. This is the parameter of interest. We
want to estimate $\lambda_i$ for each year $i$. We can do this by fitting a Poisson regression model
to the data. The Poisson regression model is as follows:

$$
\begin{align}
log(\lambda_i) &= \beta_0 + \beta_1 X_i
\end{align}
$$

where $Y_i$ is the number of landfalling hurricanes in year $i$, $X_i$ is the year, and $\lambda_i$ is 
the mean number of landfalling hurricanes in year $i$.

The inference can be done by using the `summary()` function on the model. The `summary()` function
will return the estimates of the parameters, the standard errors of the estimates, the z-statistics,
and the p-values. The p-values are used to determine if the estimates are statistically significant.

The model summary shows that the estimate of the intercept is `-4.4347989` and the estimate of the
slope is `0.0029601`. The estimate of the intercept is the log of the mean number of landfalling
hurricanes in year 0. The estimate of the slope is the log of the change in the mean number of
landfalling hurricanes per year. The standard error of the intercept is `1.6076714` and the standard
error of the slope is `0.0008266`, both resulting in a p-value of less than 0.01. Thus, we can
conclude that the estimates are statistically significant.

These estimates can be interpreted as follows. The estimate of the intercept is the log of the mean
number of landfalling hurricanes in year 0. The estimate of the slope is the log of the change in
the mean number of landfalling hurricanes per year. Thus, the mean number of landfalling
hurricanes in year 1851 is $e^{-4.4347989 + 0.0029601 * 1851} = 2.8415$. The mean number of
landfalling hurricanes in year 2022 is $e^{-4.4347989 + 0.0029601 * 2022} = 4.7139$. Thus, the
mean number of landfalling hurricanes has increased by $4.7139 - 2.8415 = 1.8724$ hurricanes
over the past 171 years. This represents a staggering 65.9% increase in the mean number of
landfalling hurricanes over the past 171 years.

Thus, we can conclude that the number of landfalling hurricanes is increasing over time. This
conclusion is supported by the fact that the mean number of landfalling hurricanes has increased
by 65.9% over the past 171 years. This conclusion is also supported by the fact that the estimate
of the slope (the log of the change in the mean number of landfalling hurricanes per year) is 
positive and statistically significant.

```{r}
#############################################
# Loading the data
#############################################

# Split the dataframe into a list of dataframes where each dataframe is a unique StormID
df <- StormR::hurdat
df_list <- split(df, df$StormID)

# Run the StormR::made_landfall_US() for each storm
landfall_index_list <- lapply(df_list, StormR::made_landfall_US)

# Clean the dataset
landfall_index_list <- unlist(landfall_index_list)
landfall_list <- df_list[landfall_index_list]
landfall_list <- lapply(landfall_list, function(x) x[, c("StormID", "Date")])
landfall_list <- lapply(landfall_list, function(x) x[!duplicated(x$StormID), ])

# Parse the date column as YYYYMMDD and create Month and Year columns
landfall_list <- lapply(landfall_list, function(x) {
  x$Date <- as.Date(x$Date, format = "%Y%m%d")
  x$month <- format(x$Date, "%m")
  x$year <- format(x$Date, "%Y")
  x
})

# Compile the cleaned data into a single dataframe
landfall_list <- lapply(landfall_list, function(x) x[, -2])
df <- do.call(rbind, landfall_list)
rownames(df) <- NULL

# Collapse the data to yearly counts, counting occurrences of each year using aggregate()
landfall_df <- aggregate(df$year, by = list(df$year), FUN = length)

#############################################
# Conducting preliminary analysis and EDA
#############################################

par(mfrow = c(2, 1))

# Plot the yearly counts as a scatterplot
plot(landfall_df$Group.1, landfall_df$x, xlab = "Year", ylab = "Number of Landfalling Hurricanes", main = "Number of Landfalling Hurricanes by Year")

# Plot a histogram of the yearly counts
hist(landfall_df$x, xlab = "Number of Landfalling Hurricanes", ylab = "Frequency", main = "Histogram of Number of Landfalling Hurricanes by Year", breaks = seq(0, 14, 1), prob = TRUE)
lines(0:max(landfall_df$x), dpois(0:max(landfall_df$x), mean(landfall_df$x)), col = 'red')

# Print the mean and variance of the yearly counts
print(paste("Mean:", mean(landfall_df$x)))
print(paste("Variance:", var(landfall_df$x)))

#############################################
# Fitting a Poisson regression model
#############################################

# Clean the data for the model
colnames(landfall_df) <- c("Year", "Count")
landfall_df$Year <- as.numeric(landfall_df$Year)

# Run a poisson regression model
landfall_model <- glm(Count ~ Year, data = landfall_df, family = "poisson")
summary(landfall_model)

# Plot the model on a scatterplot of data
par(mfrow = c(1, 1))
plot(landfall_df$Year, landfall_df$Count, xlab = "Year", ylab = "Number of Landfalling Hurricanes", main = "Number of Landfalling Hurricanes by Year")

# Add a regression line to the plot
predProbs<-predict(landfall_model, data.frame(Year=seq(min(landfall_df$Year), max(landfall_df$Year), length.out=1000)), type="response")
lines(seq(min(landfall_df$Year), max(landfall_df$Year), length.out=1000), predProbs, col=2, lwd=2)
```

# Is the intensity of tropical cyclones increasing over time?

In this question, we try to estimate the change in the intensity of tropical cyclones over time.

```{r}
#############################################
# Loading the data
#############################################

# Split the dataframe into a list of dataframes where each dataframe is a unique StormID
df <- StormR::hurdat
df <- df[1:40, ]

df_list <- split(df, df$StormID)
df_list <- df_list[1:4]

# Run the StormR::calculate_cyclone_energy() for each storm
cyclone_energy_list <- lapply(df_list, StormR::calculate_cyclone_energy)
cyclone_energy_list

# Clean the dataset
cyclone_energy_list <- unlist(cyclone_energy_list)
df <- df[!duplicated(df$StormID), ]
df <- df[, c("StormID", "Date")]
df <- cbind(df, cyclone_energy_list)
colnames(df) <- c("StormID", "Date", "CycloneEnergy")
rownames(df) <- NULL

# Parse the date column as YYYYMMDD and create Month and Year columns
df$Date <- as.Date(df$Date, format = "%Y%m%d")
df$Month <- format(df$Date, "%m")
df$Year <- format(df$Date, "%Y")
df <- df[, -2]

#############################################
# Conducting preliminary analysis and EDA
#############################################

par(mfrow = c(2, 1))

# Plot the yearly counts as a scatterplot
plot(df$year, df$CycloneEnergy, xlab = "Year", ylab = "Cyclone Energy", main = "Cyclone Energy by Year")

# Plot a histogram of the yearly counts
hist(df$CycloneEnergy, xlab = "Cyclone Energy", ylab = "Frequency", main = "Histogram of Cyclone Energy by Year", breaks = seq(0, 14, 1), prob = TRUE)

```