---
title: "Analysis"
output: 
  rmarkdown::html_vignette:
    fig_height: 7
    fig_width: 7
vignette: >
  %\VignetteIndexEntry{Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StormR)
library(ggforce)

# Set Graphics
par(mfrow = c(1, 1))
```

# Problem 1 
Plot the tracks of the storms in 2020, 2021, and 2022 in 3 separate plots. Your plots will be graded for how easy they are to decipher and how much information they display. Include, for example, some way to identify which storm each track belongs to.
```{r}
#Cut dataframe to only storms for that year
storm_data_2020 <- hurdat[substr(hurdat$Date, start=1, stop=4) == "2020",]
storm_data_2021 <- hurdat[substr(hurdat$Date, start=1, stop=4) == "2021",]
storm_data_2022 <- hurdat[substr(hurdat$Date, start=1, stop=4) == "2022",]

#Function to get a list of individual storms for that year
get_separated_storms <- function(df){
  list_of_storms <- list()
  new_storm_dataframe <- df[1,]
  current_storm_id <- df$StormID[1]
  for(i in 2:nrow(df)){
    if (df$StormID[i] != current_storm_id){
      #update current storm ID
      current_storm_id <- df$StormID[i]
      #append old data frame to list_of_storms
      list_of_storms <- append(list_of_storms, list(new_storm_dataframe))
      #update new data frame
      new_storm_dataframe <- df[i,]
    } else{
      new_storm_dataframe <- rbind(new_storm_dataframe, df[i,])
    }
  }
  return(list_of_storms)
}

#List of individual storms for each year
individual_storms_2020 <- get_separated_storms(storm_data_2020)
individual_storms_2021 <- get_separated_storms(storm_data_2021)
individual_storms_2022 <- get_separated_storms(storm_data_2022)

individual_storms_2020 <- lapply(individual_storms_2020, interpolate_storm_track)
individual_storms_2021 <- lapply(individual_storms_2021, interpolate_storm_track)
individual_storms_2022 <- lapply(individual_storms_2022, interpolate_storm_track)

#Plot 2020 Storms
StormR::plot_storm_track(individual_storms_2020)
#Plot 2021 Storms
StormR::plot_storm_track(individual_storms_2021)
#Plot 2022 Storms
StormR::plot_storm_track(individual_storms_2022)
```

# Problem 2
```{r}
#Cut dataframe to individual hurricanes for that year
storm_data_Katrina <- hurdat[substr(hurdat$Date, start=1, stop=4) == "2005"
                             & hurdat$StormName == "KATRINA",]
storm_data_Sandy <- hurdat[substr(hurdat$Date, start=1, stop=4) == "2012"
                           & hurdat$StormName == "SANDY",]
storm_data_Harvey <- hurdat[substr(hurdat$Date, start=1, stop=4) == "2017"
                            & hurdat$StormName == "HARVEY",]
storm_data_Ian <- hurdat[substr(hurdat$Date, start=1, stop=4) == "2022"
                         & hurdat$StormName == "IAN",]

made_landfall_frame <- function(df){
  to_return <- data.frame()
  for(i in 1:nrow(df)){
    if(made_landfall_US(df[i,]) == TRUE){
      to_return <- rbind(to_return, df[i,])
    }
  }
  return(to_return)
}

landfall_Katrina <- made_landfall_frame(storm_data_Katrina)
landfall_Sandy <- made_landfall_frame(storm_data_Sandy)
landfall_Harvey <- made_landfall_frame(storm_data_Harvey)
landfall_Ian <- made_landfall_frame(storm_data_Ian)

pick_strongest <- function(df){
  new_strongest <- df[df$MaximumWind == max(df$MaximumWind),]
  if(nrow(new_strongest) == 1){
    return(new_strongest)
  }
  #Eliminate rows where there's no data for maximum extent
  to_return <- data.frame()
  for (i in 1:nrow(new_strongest)){
    if (new_strongest[i,]$`34NE` != -999){
      to_return <- rbind(to_return, new_strongest[i,])
    }
  }
  if(nrow(to_return) != 0){
    return(to_return[1,])
  }
  return(new_strongest[1,])
}

strongest_Katrina <- pick_strongest(landfall_Katrina)
strongest_Sandy <- pick_strongest(landfall_Sandy)
strongest_Harvey <- pick_strongest(landfall_Harvey)
strongest_Ian <- pick_strongest(landfall_Ian)

all_together <- rbind(strongest_Katrina, strongest_Sandy,
                      strongest_Harvey, strongest_Ian)


par(mfrow = c(1,2))

plot_storm_pos_and_size(strongest_Katrina)
plot_storm_track(storm_data_Katrina)

plot_storm_pos_and_size(strongest_Sandy)
plot_storm_track(storm_data_Sandy)

plot_storm_pos_and_size(strongest_Harvey)
plot_storm_track(storm_data_Harvey)

plot_storm_pos_and_size(strongest_Ian)
plot_storm_track(storm_data_Ian)

plot_storm_pos_and_size(all_together)
```


# Problem 3
Create a dataframe that has one row for each individual storm, with the following columns:
- storm id
- storm name
- maximum wind speed
- minimum pressure
- indicator for whether it made landfall or not
- accumulated cyclone energy
```{r}
max_wind_speed <- function(df){
  current_max <- df$MaximumWind[1]
  if(nrow(df) == 1){
    return(current_max)
  }
  for(i in 2:nrow(df)){
    if(df$MaximumWind[i] > current_max){
      current_max <- df$MaximumWind[i]
    }
  }
  return(current_max)
}

minimum_pressure <- function(df){
  current_min <- df$MinimumPressure[1]
  if(nrow(df) == 1){
    return(current_min)
  }
  for(i in 2:nrow(df)){
    if(df$MinimumPressure[i] < current_min){
      current_min <- df$MinimumPressure[i]
    }
  }
  return(current_min)
}

list_of_storms <- split(hurdat, hurdat$StormID)
new_data <- data.frame()
for(i in 1:length(list_of_storms)){
  storm_id <- list_of_storms[[i]]$StormID[1]
  storm_name <- list_of_storms[[i]]$StormName[1]
  max_wind <- max_wind_speed(list_of_storms[[i]])
  min_pressure <- minimum_pressure(list_of_storms[[i]])
  made_landfall <- made_landfall_US(list_of_storms[[i]])
  cyclone <- calculate_cyclone_energy(list_of_storms[[i]])
  
  new_row <- data.frame(StormID = storm_id, StormName = storm_name,
                        MaxWindSpeed = max_wind, MinimumPressure = min_pressure,
                        MadeLandfall = made_landfall, 
                        AccumulatedCycloneEnergy = cyclone)
  new_data <- rbind(new_data, new_row)
}

head(new_data)
```

# Problem 4
Plots exploring interesting things in dataset 
```{r}
#Remove missing data
plot_data <- subset(new_data, MaxWindSpeed != -999 & MinimumPressure != -999)

#Draw Graphs
plot(plot_data$MinimumPressure, plot_data$AccumulatedCycloneEnergy, 
     xlab = "MinimumPressure", ylab = "Accumulated Cyclone Energy")
abline(lm(AccumulatedCycloneEnergy ~ MinimumPressure, data = plot_data))
plot(plot_data$MaxWindSpeed, plot_data$AccumulatedCycloneEnergy, 
     xlab= "Maximum Wind Speed", ylab = "Accumulated Cyclone Energy")
abline(lm(AccumulatedCycloneEnergy ~ MaxWindSpeed, data = plot_data))
plot(plot_data$MaxWindSpeed, plot_data$MinimumPressure,
     xlab = "Maximum Wind Speed", ylab = "Minimum Pressure")
abline(lm(MinimumPressure ~ MaxWindSpeed, data = plot_data))

#Other plots were tried that didn't seem as sensible
#plot(new_data$MaxWindSpeed, new_data$MadeLandfall)
#plot(new_data$MinimumPressure, new_data$MadeLandfall, xlim = c(850, 1000))
#plot(new_data$MadeLandfall, new_data$AccumulatedCycloneEnergy)

```

In the above data, we used the dataset that we compiled in problem 3 and then
conducted further analysis using plots as well as their regression lines. 

From the first chart, we note that as the minimum pressure of a storm increases,
the accumulated cyclone energy of the storm decreases in both expectation as
well as variance. This suggests that when considering these two variables,
the data is heteroskedastic as the variance of ACE is also dependent on 
minimum pressure. Finally, the decreasing trend suggests that ACE and 
minimum pressure are negatively correlated.

In the second chart, we note that as the maximum wind speed increases, 
the accumulated cyclone energy of the storm increases in both expectation
as well as variance. This suggests that the data is heteroskedastic 
meaning that as maximum wind speed increases, the variance of ACE also increases.
Further, the increasing trend suggests that there is a positive correlation
between maximum wind speed and accumulated cyclone energy.

Finally, in the third chart, we note that as maximum wind speed increases,
the minimum pressure has a downward trend. This suggests that there is a 
negative correlation between maximum wind speed and accumulated cyclone energy.

# Is the number of landfalling hurricanes increasing over time? 

In this question, we try to estimate the change in the number of landfalling hurricanes over time.
Here, we will use the Hurdat dataset to answer this question. The Hurdat dataset contains
information about all the hurricanes that have occurred in the Atlantic Ocean since 1851. 

Given the large heterogeneity in the number of hurricanes that occur each month, we will
collapse the data to yearly counts, counting occurrences of each year. We will then plot the
yearly counts as a scatterplot and a histogram. We do this to understand the distribution of
the yearly counts. 

Per theory (that the number of hurricane landfalls in a year is count data), we expect the
distribution of the yearly counts to be Poisson. We can test this by observing the histogram
of the yearly counts and comparing it to the Poisson distribution overlayed on the plot. We also note that the
mean and variance of the yearly counts are similar, as theory predicts.

Thus, we can conclude that the yearly counts are Poisson distributed. Given this information, we
can fit a Poisson regression model to the data. We will use the year as the predictor variable
and the yearly counts as the response variable. We will then plot the model on a scatterplot
of the data. 

The Poisson regression model is a generalized linear model (GLM) that assumes the response
variable is Poisson distributed. The Poisson distribution is a discrete probability distribution
that expresses the probability of a given number of events occurring in a fixed interval of time
or space if these events occur with a known constant mean rate and independently of the time
since the last event. The Poisson distribution can be used to model the number of events
occurring in a given time interval.

The Poisson regression model specified in this question is as follows, where $Y_i$ is the number
of landfalling hurricanes in year $i$, $X_i$ is the year, and $\lambda_i$ is the mean number of
landfalling hurricanes in year $i$: 

$$
\begin{align}
Y_i &\sim Poisson(\lambda_i) \\
\end{align}
$$

Thus, the mean of the Poisson distribution is $\lambda_i$. This is the parameter of interest. We
want to estimate $\lambda_i$ for each year $i$. We can do this by fitting a Poisson regression model
to the data. The Poisson regression model is as follows:

$$
\begin{align}
log(\lambda_i) &= \beta_0 + \beta_1 X_i
\end{align}
$$

where $Y_i$ is the number of landfalling hurricanes in year $i$, $X_i$ is the year, and $\lambda_i$ is 
the mean number of landfalling hurricanes in year $i$.

The inference can be done by using the `summary()` function on the model. The `summary()` function
will return the estimates of the parameters, the standard errors of the estimates, the z-statistics,
and the p-values. The p-values are used to determine if the estimates are statistically significant.

The model summary shows that the estimate of the intercept is `-4.4347989` and the estimate of the
slope is `0.0029601`. The estimate of the intercept is the log of the mean number of landfalling
hurricanes in year 0. The estimate of the slope is the log of the change in the mean number of
landfalling hurricanes per year. The standard error of the intercept is `1.6076714` and the standard
error of the slope is `0.0008266`, both resulting in a p-value of less than 0.01. Thus, we can
conclude that the estimates are statistically significant.

These estimates can be interpreted as follows. The estimate of the intercept is the log of the mean
number of landfalling hurricanes in year 0. The estimate of the slope is the log of the change in
the mean number of landfalling hurricanes per year. Thus, the mean number of landfalling
hurricanes in year 1851 is $e^{-4.4347989 + 0.0029601 * 1851} = 2.8415$. The mean number of
landfalling hurricanes in year 2022 is $e^{-4.4347989 + 0.0029601 * 2022} = 4.7139$. Thus, the
mean number of landfalling hurricanes has increased by $4.7139 - 2.8415 = 1.8724$ hurricanes
over the past 171 years. This represents a staggering 65.9% increase in the mean number of
landfalling hurricanes over the past 171 years.

Thus, we can conclude that the number of landfalling hurricanes is increasing over time. This
conclusion is supported by the fact that the mean number of landfalling hurricanes has increased
by 65.9% over the past 171 years. This conclusion is also supported by the fact that the estimate
of the slope (the log of the change in the mean number of landfalling hurricanes per year) is 
positive and statistically significant.

```{r}
#############################################
# Loading the data
#############################################

# Split the dataframe into a list of dataframes where each dataframe is a unique StormID
df <- StormR::hurdat
df_list <- split(df, df$StormID)

# Run the StormR::made_landfall_US() for each storm
landfall_index_list <- lapply(df_list, StormR::made_landfall_US)

# Clean the dataset
landfall_index_list <- unlist(landfall_index_list)
landfall_list <- df_list[landfall_index_list]
landfall_list <- lapply(landfall_list, function(x) x[, c("StormID", "Date")])
landfall_list <- lapply(landfall_list, function(x) x[!duplicated(x$StormID), ])

# Parse the date column as YYYYMMDD and create Month and Year columns
landfall_list <- lapply(landfall_list, function(x) {
  x$Date <- as.Date(x$Date, format = "%Y%m%d")
  x$month <- format(x$Date, "%m")
  x$year <- format(x$Date, "%Y")
  x
})

# Compile the cleaned data into a single dataframe
landfall_list <- lapply(landfall_list, function(x) x[, -2])
df <- do.call(rbind, landfall_list)
rownames(df) <- NULL

# Collapse the data to yearly counts, counting occurrences of each year using aggregate()
landfall_df <- aggregate(df$year, by = list(df$year), FUN = length)

#############################################
# Conducting preliminary analysis and EDA
#############################################

par(mfrow = c(2, 1))

# Plot the yearly counts as a scatterplot
plot(landfall_df$Group.1, landfall_df$x, 
     xlab = "Year", ylab = "Number of Landfalling Hurricanes", 
     main = "Number of Landfalling Hurricanes by Year")

# Plot a histogram of the yearly counts
hist(landfall_df$x, xlab = "Number of Landfalling Hurricanes", ylab = "Frequency",
     main = "Histogram of Number of Landfalling Hurricanes by Year", 
     breaks = seq(0, 14, 1), prob = TRUE)
lines(0:max(landfall_df$x), dpois(0:max(landfall_df$x), mean(landfall_df$x)),
      col = 'red')

# Print the mean and variance of the yearly counts
print(paste("Mean:", mean(landfall_df$x)))
print(paste("Variance:", var(landfall_df$x)))

#############################################
# Fitting a Poisson regression model
#############################################

# Clean the data for the model
colnames(landfall_df) <- c("Year", "Count")
landfall_df$Year <- as.numeric(landfall_df$Year)

# Run a poisson regression model
landfall_model <- glm(Count ~ Year, data = landfall_df, family = "poisson")
summary(landfall_model)

# Plot the model on a scatterplot of data
par(mfrow = c(1, 1))
plot(landfall_df$Year, landfall_df$Count, 
     xlab = "Year", ylab = "Number of Landfalling Hurricanes", 
     main = "Number of Landfalling Hurricanes by Year")

# Add a regression line to the plot
predProbs<-predict(landfall_model, data.frame(Year=seq(min(landfall_df$Year), max(landfall_df$Year), length.out=1000)), type="response")
lines(seq(min(landfall_df$Year), max(landfall_df$Year), length.out=1000), 
      predProbs, col=2, lwd=2)
```

# Is the intensity of tropical cyclones increasing over time?

In this question, we try to estimate the change in the intensity of tropical cyclones over time.
Here, we will use the Hurdat dataset to answer this question. The Hurdat dataset contains
information about all the hurricanes that have occurred in the Atlantic Ocean since 1851.

Given the large heterogeneity in the intensity of tropical cyclones that occur each month, we will
collapse the data to yearly counts, counting occurrences of each year. We will then plot the
yearly counts as a scatterplot and a histogram. We do this to understand the distribution of
the yearly counts.

Per theory (that the intensity of tropical cyclones in a year is continuous data), we expect the
distribution of the yearly counts to be normal. We can test this by observing the histogram of
the yearly counts and comparing it to the normal distribution overlayed on the plot.

Thus, we can conclude that the yearly counts are normally distributed. Given this information, we
can fit a normal regression model to the data. We will use the year as the predictor variable
and the yearly counts as the response variable. We will then plot the model on a scatterplot
of the data.

The normal regression model is a generalized linear model (GLM) that assumes the response
variable is normally distributed. The normal distribution is a continuous probability distribution
that expresses the probability density of a given number of events occurring in a fixed interval of time
or space if these events occur with a known constant mean rate and independently of the time
since the last event. The normal distribution can be used to model the intensity of tropical cyclones.

The normal regression model specified in this question is as follows, where $Y_i$ is the intensity
of tropical cyclones in year $i$, $X_i$ is the year, and $\mu_i$ is the mean intensity of tropical
cyclones in year $i$:

$$
\begin{align}
Y_i &\sim Normal(\mu_i, \sigma^2) \\
\end{align}
$$

Thus, the mean of the normal distribution is $\mu_i$ and the variance of the normal distribution is $\sigma^2$.

This is the parameter of interest. We want to estimate $\mu_i$ for each year $i$. We can do this by fitting a normal regression model
to the data. The normal regression model is as follows:

$$
\begin{align}
\mu_i &= \beta_0 + \beta_1 X_i
\end{align}
$$

where $Y_i$ is the intensity of tropical cyclones in year $i$, $X_i$ is the year, and $\mu_i$ is
the mean intensity of tropical cyclones in year $i$.

The inference can be done by using the `summary()` function on the model. The `summary()` function
will return the estimates of the parameters, the standard errors of the estimates, the t-statistics,
and the p-values. The p-values are used to determine if the estimates are statistically significant.

The model summary shows that the estimate of the intercept is `-7.794059` and the estimate of the
slope is `0.008379`. The estimate of the intercept is the mean intensity of tropical cyclones in year 0.
The estimate of the slope is the change in the mean intensity of tropical cyclones per year. 
The standard error of the intercept is `13.760788` and the standard error of the slope is `0.007104`,
both resulting in a p-value of greater than 0.1. Thus, we can conclude that the estimates are not
statistically significant. 

These estimates can be interpreted as follows. The estimate of the intercept is the mean intensity
of tropical cyclones in year 0. The estimate of the slope is the change in the mean intensity of
tropical cyclones per year. However, since the estimates are not statistically significant, we cannot
interpret them. Thus, we cannot interpret the mean intensity of tropical cyclones in year 0 or the
change in the mean intensity of tropical cyclones per year.

Thus, we cannot conclude that the intensity of tropical cyclones is increasing over time. This
conclusion is supported by the fact that the estimates of the intercept and slope are not statistically
significant. Thus, we fail to reject our null hypothesis that the intensity of tropical cyclones is not
increasing over time.

```{r}
#############################################
# Loading the data
#############################################

# Split the dataframe into a list of dataframes where each dataframe is a unique StormID
df <- StormR::hurdat
df_list <- split(df, df$StormID)

# Run the StormR::calculate_cyclone_energy() for each storm
cyclone_energy_list <- lapply(df_list, StormR::calculate_cyclone_energy)

# Clean the dataset
cyclone_energy_list <- unlist(cyclone_energy_list)
df <- df[!duplicated(df$StormID), ]
df <- df[, c("StormID", "Date")]
df <- cbind(df, cyclone_energy_list)
colnames(df) <- c("StormID", "Date", "CycloneEnergy")
rownames(df) <- NULL

# Parse the date column as YYYYMMDD and create Month and Year columns
df$Date <- as.Date(df$Date, format = "%Y%m%d")
df$Month <- format(df$Date, "%m")
df$Year <- format(df$Date, "%Y")
df <- df[, -2]

#############################################
# Conducting preliminary analysis and EDA
#############################################

par(mfrow = c(2, 1))

# Aggregate the data at the year level
df <- aggregate(df$CycloneEnergy, by = list(df$Year), FUN = mean)
colnames(df) <- c("Year", "CycloneEnergy")

# Plot the yearly counts as a scatterplot and a histogram
plot(df$Year, df$CycloneEnergy, xlab = "Year", ylab = "Cyclone Energy",
     main = "Cyclone Energy by Year")
hist(df$CycloneEnergy, xlab = "Cyclone Energy", ylab = "Frequency",
     main = "Histogram of Cyclone Energy by Year")

# Mean and variance of the yearly counts
print(paste("Mean:", mean(df$CycloneEnergy)))
print(paste("Variance:", var(df$CycloneEnergy)))

#############################################
# Fitting a normal regression model
#############################################

# Clean the data for the model
df$Year <- as.numeric(df$Year)

# Run a normal regression model
cyclone_energy_model <- lm(CycloneEnergy ~ Year, data = df)
summary(cyclone_energy_model)

# Plot the model on a scatterplot of data
par(mfrow = c(1, 1))
plot(df$Year, df$CycloneEnergy, xlab = "Year", ylab = "Cyclone Energy", 
     main = "Cyclone Energy by Year")

# Add a regression line to the plot
abline(cyclone_energy_model, col = "red")
```

# Is the maximum wind speed of tropical cyclones increasing over time?

We have seen that there exists no trend in the intensity of tropical cyclones over time. However,
we have not yet investigated the maximum wind speed of tropical cyclones over time. Per this 
WashingtonPost article (https://www.washingtonpost.com/climate-environment/interactive/2023/hurricane-risk-map-us-climate/),
the maximum wind speed of tropical cyclones is increasing over time. Thus, we will investigate this
claim.

More specifically, we will control for system status (whether the tropical cyclone was a tropical
depression, tropical storm, or hurricane) and investigate if the maximum wind speed of tropical
cyclones is increasing over time across all systems. We will use the Hurdat dataset to answer this
question. The Hurdat dataset contains information about all the hurricanes that have occurred in
the Atlantic Ocean since 1851.

We first start by running a linear regression model with the maximum wind speed as the response
variable and the year as the predictor variable. We see that there exists a statistically significant
positive relationship between the year and the maximum wind speed. However, we have not yet
controlled for system status. It might be likely that this effect is not due to the maximum wind speed 
of tropical cyclones increasing over time, but rather due to the fact that the proportion of hurricanes 
and stronger storms has increased over time. Thus, we will control for system status.

We then run a linear regression model with the maximum wind speed as the response variable, the
year as the predictor variable, and fixed effects for system status. We see that there does not 
exist a statistically significant relationship between the year and the maximum wind speed. Thus,
we can conclude that the maximum wind speed of tropical cyclones is not increasing over time - instead 
the proportion of hurricanes and stronger storms has increased over time.

An assumption of this hypothesis is the some types of tropical storms have higher maximum wind
speeds than others. Thus, we will investigate this assumption by regressing maximum wind speed
on system status. We see that there exists a statistically significant relationship between system
status and maximum wind speed. Thus, we can conclude that some types of tropical storms have
higher maximum wind speeds than others.

Finally, we visually confirm the hypothesis by plotting the distribution of system status by year
for each system status level. We see that the proportion of hurricanes and stronger storms has
increased over time. Thus, we can conclude that the proportion of hurricanes and stronger storms
has increased over time.

Thus, we can conclude that the maximum wind speed of tropical cyclones is not increasing over
time - instead the proportion of hurricanes and stronger storms has increased over time. This
does lead to an average increase in the maximum wind speed of tropical cyclones over time, as noted 
by our linear regression model. Thus, as the WashingtonPost article notes, the maximum wind speed
of tropical cyclones is increasing over time. However, this is not exactly true, as the maximum wind
speed of tropical cyclones is not increasing over time when controlling for system status. Instead, 
hurricanes which have higher maximum wind speeds are becoming more common over time.

```{r}
#############################################
# Loading the data
#############################################

# Keep the StormID, Date, SystemStatus, and MaximumWind columns
df <- StormR::hurdat[, c("StormID", "Date", "SystemStatus", "MaximumWind")]

# Parse the date column as YYYYMMDD and create Month and Year columns
df$Date <- as.Date(df$Date, format = "%Y%m%d")
df$Month <- format(df$Date, "%m")
df$Year <- format(df$Date, "%Y")
df <- df[, -2]

# Convert Year to numeric
df$Year <- as.numeric(df$Year)
df$SystemStatus <- gsub(" ", "", df$SystemStatus)
df$SystemStatus <- as.factor(df$SystemStatus)

#############################################
# Conducting Analysis
#############################################

# Run a linear regression model
library(lfe)
model <- felm(MaximumWind ~ Year, data = df)
summary(model)

# Run a linear regression model with fixed effects for SystemStatus
model <- felm(MaximumWind ~ Year | SystemStatus, data = df)
summary(model)

# Run a linear regression model with fixed effects
model <- felm(MaximumWind ~ SystemStatus, data = df)
summary(model)

# Plot 8 plots in a 4x2 grid, 
# showing the histogram distribution of SystemStatus by Year
# for 8 SystemStatus levels at the same axis
par(mfrow = c(4, 2))
for (i in 1:8) {
  hist(df[df$SystemStatus == levels(df$SystemStatus)[i], ]$Year, 
       xlab = "Year", ylab = "Frequency", 
       main = paste("Histogram of", levels(df$SystemStatus)[i], "by Year"), 
       breaks = seq(1850, 2025, 5), prob = TRUE, xlim = c(1850, 2050))
}
```
